Our Galactic Midplane Is Probably Wrong, and Not by a Little

### 2019-01-29 paper/ms.tex
Update Rn plot caption

\begin{figure*}
\plotone{fig/Rn_vs_mc.pdf}
\caption{The neighborhood around an open cluster of mass $m_c$ for the thin,
and thick orbits (\thincolor and \thickcolor, respectively; see
Table~\ref{tab:orbits}) and for each of the FIRE galaxies considered here ---
m12i, m12f, and m12m ({\em left}, {\em center}, and {\em right} panels,
respectively). Given the $z$ offset for a cluster of mass $m_c$ computed in
Figure~\ref{fig:cluster_offset}, we convert this to a chord length using the
result from Figure~\ref{fig:range_deltaphi} and plot as a solid blue line. We
interpret this chord length as the ``neighborhood'' around the cluster, i.e.
the distance from the cluster one could go before the $J_z$ error induced by
our midplane effect is comparable to the intrinsic action dispersion of the
cluster. When the $z$ offset is larger than the maximum range in
Figure~\ref{fig:range_deltaphi}, we report the maximum chord length
($2\times8.2\,\kpc$). We aso report the same procedure but using the
$\pm1\sigma$ lines from Figure~\ref{fig:range_deltaphi}, which we plot here as
dashed lines. For the medium- and high-$J_z$ orbits (orange and red), the
neighborhood is quite large and thus the effect is negligible. However, for
the low-$J_z$ orbit (blue), which is closest to the orbits of nearby open
clusters (see Table~\Gus{x}), the neighborhood is only a few hundred $\pc$ for
low-mass clusters.}
\label{fig:Rn_mc}
\end{figure*}

>>>>

\begin{figure*}
\plotone{fig/Rn_vs_mc.pdf}
\caption{The neighborhood around an open cluster of mass $m_c$ for the thin,
and thick orbits (\thincolor and \thickcolor, respectively; see
Table~\ref{tab:orbits}) and for each of the FIRE galaxies considered here ---
m12i, m12f, and m12m ({\em left}, {\em center}, and {\em right} panels,
respectively). Given the $z$ offset for a cluster of mass $m_c$ computed in
Figure~\ref{fig:cluster_offset}, we convert this to a chord length using the
result from Figure~\ref{fig:range_deltaphi}. We interpret this chord length as
the ``neighborhood'' around the cluster, i.e. the distance from the cluster
one could go before the $J_z$ error induced by our midplane effect is
comparable to the intrinsic action dispersion of the cluster. When the $z$
offset is larger than the maximum range in Figure~\ref{fig:range_deltaphi}, we
report the maximum chord length ($2\times8.2\,\kpc$). We aso report the same
procedure but using the $\pm1\sigma$ lines from
Figure~\ref{fig:range_deltaphi}, which we plot here as dashed lines. For the
thick orbit (\thickcolor), the neighborhood is quite large and thus the effect
is negligible. However, for the thin orbit (\thincolor), which is closest to
the orbits of nearby open clusters (see Table~\ref{tab:real_clusters}), the
neighborhood is only a few hundred $\pc$ for low-mass clusters.}
\label{fig:Rn_mc}
\end{figure*}
